Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-17 paper/manuscript.Rmd
insert fogo deets

<!-- Caribou were introduced to Fogo Island (n = 26 animals between 1964–67) and
Change Island (n = 5 animals in 1964) from the main Island of Newfoundland as
part of a series of translocations and introductions throughout the province
(Bergerud & Mercer 1989). -->

@@

Forage limitation and over-grazing is a major concern for caribou populations
[@Schaefer2016] and could explain movement between islands. Conspecific
competition for resources driven by reduced foraging opportunities can decrease
reproductive success of adult females [@Schaefer2016]. Forage scarcity has been
proposed as a potential reason for caribou moving between arctic islands on the
sea-ice in winter [@Miller1977]. For very small islands, over-grazing by newly
arrived caribou may rapidly deplete forage [@Bergerud1990]. Without sea ice,
movement from the mainland to an island, or between islands, requires caribou to
assess the trade-off associated with swimming.

>>>>

@@

Forage limitation and over-grazing is a major concern for caribou populations
[@Schaefer2016] and could explain movement between islands. Conspecific
competition for resources driven by reduced foraging opportunities can decrease
reproductive success of adult females [@Schaefer2016].Forage scarcity has been
proposed as a potential reason for caribou moving between arctic islands on the
sea-ice in winter [@Miller1977]. Caribou were introduced to Fogo Island (n = 26
animals between 1964–67) and Change Island (n = 5 animals in 1964) from
Newfoundland as part of a series of translocations and introductions throughout
the province (Bergerud & Mercer 1989). It is unknown when caribou began
colonizing nearby islands, but given that some are small, it is likely forage is
depleted relatively quickly. While forage depletion is possible for Fogo Island,
For very small islands, over-grazing by newly arrived caribou may rapidly
deplete forage [@Bergerud1990].

Without sea ice,
movement from the mainland to an island, or between islands, requires caribou to
assess the trade-off associated with swimming.
